Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2014-12-15 content/background.tex
pass through section 3

\section{Background}\label{sec:bg}
%The purpose of the correlated-calls analysis is to solve IFDS problems more precisely than using the standard IFDS algorithm by ruling out some infeasible paths. The correlated-calls analysis works by transforming an IFDS problem to an IDE problem, solving the IDE problem, and transforming the IDE result to a solution to the original IFDS problem. 
This section defines basic terminology and presents the IFDS and IDE algorithms.
\ftodo{
  Shall we add a sentence saying that readers familiar with these algorithms may skip this section?
}

\subsection{Terminology and Notation}
%We will start by introducing several concepts used by the IFDS and IDE analyses.
The \textit{control-flow graph} of a procedure is a directed graph whose nodes are instructions, and which contains an edge from $n_1$ to $n_2$ whenever
$n_2$ may execute immediately after $n_1$. A CFG has a distinguished \textit{start node} \textsf{start}$_p$ and \textit{end node} \textsf{end}$_p$.
%and edges represent transfer of control between the instructions during an execution of the program. 
%A control-flow graph has a unique start node, $\startmain$, which is the node corresponding to the program entrypoint.
%An \textit{intra-procedural} path is a path in a control-flow graph whose nodes are in the same procedure. By contrast, an \textit{inter-procedural path} is one that contains nodes from different procedures. 
The \textit{control-flow supergraph} of a program contains the CFGs of all of the procedures as
subgraphs. In addition, for each call instruction $c$, the supergraph contains a \textit{call-to-start} edge to the start node of every procedure that
may be called from $c$, and an \textit{end-to-return} edge from the end node of the procedure back to the call instruction.
\otodo{do we really need to extra "return nodes" that the IFDS/IDE papers add?}
%is a control-flow graph
%in which each procedure $p$ is augmented with an additional \textit{start node} \textsf{start}$_p$ and \textit{end node} \textsf{end}$_p$, and for each call $c_q$ to a procedure $q$, there is a \textit{call node} \textsf{call}$_{c_q}$ and subsequent \textit{return node} \textsf{return}$_{c_q}$.

@@

\otodo{do we ever use $\src$ and $\target$?}
We denote the source and end nodes of a graph edge $e$ as $\src e$ and $\target e$.

@@

A path through the control-flow supergraph is \textit{valid} if every end-to-return edge on the path returns
to the site of the most recent unmatched call. 
\ftodo{Can we explain/define the notion of the ``most recent unmatched call'' more precisely?}
The set of all valid paths from the program entry point to
a node $n$ is denoted $\ivp(n)$.
\otodo{Should we give a formal definition?}

@@

\otodo{The definitions that Marianna had were for \emph{complete}
lattices/semilattices. All of the lattices in the context of IFDS/IDE
are/must be complete. I'll just say that here.}
\ftodo{Would it make sense to first the define the notion of a lattice without referring to its completeness?
       This could be followed by defining what it means for a (semi)lattice to be complete, and then we
       could say that all lattices considered in this paper are complete, etc.}
%\ftodo{Can we define the symbols $\sqcup$ and $\sqcap$ for join and meet here?}
A \textit{complete lattice} is a partially ordered set $(S,\sqsubseteq)$ in which every subset has a least upper bound, called \textit{join} or $\sqcup$, and a greatest lower bound, called \textit{meet} or $\sqcap$.
A \textit{complete meet semilattice} is a partially ordered set in which every subset need only have a greatest lower bound.
The symbols $\bot$ and $\top$ are used to denote the greatest lower bound of $S$ and of the empty set, respectively.
Since all of the (semi)lattices discussed in this paper are required to be complete, we will henceforth leave out the
\textit{complete} qualifier.

@@

%On the exploded graph, the composition of two functions is represented by the paths that are formed when the exploded-graph edges are combined.
\otodo{The example used to say $R_f \circ R_g$, but I believe it showed $R_g \circ R_f$. I fixed it, but please check that this is correct.}

@@

In this way, the IFDS algorithm reduces the input data-flow problem to a graph-reachability problem.
\begin{example}
  In a taint analysis, $D$ is the set of variables in the program. If a fact $d\in D$ is reachable at a given node, then the variable is considered secret at that node. Otherwise, it is considered not secret. The question ``is $d$ secret at node $n$?'' becomes ``is there a realizable path from (\textsf{start}$_\texttt{main}$,\,\textbf{0}) to $(n,\,d)$?''.
\end{example}
\commentout{\begin{example} 
  In an available-expressions analysis, $D$ is the set of all expressions in the program. If an expression $d\in D$ is reachable at a certain node, it means that it does not need to be recomputed at that node. 
\end{example}}
}
\begin{example}
  The exploded supergraph for Listing~\ref{list:ccexample} is shown in Figure~\ref{fig:cc_edgefn_example}.\mtodo{Tell the reader here to ignore the labels on the edges of the graph?}
  We can see that there is a realizable path
  from the start node of the exploded graph to the variable \verb's' at~the~node~$\textsf{print(s)}$ in the \verb'B.bar' method. This means that at that node, \verb's' is considered secret.

@@

\begin{figure}
  \centering
    \tikzstyle{n}=[fill=black,circle,inner sep=1.5pt,sm]
    \tikzstyle{sm}=[font=\footnotesize]
\begin{tikzpicture}[>=stealth,on grid, auto]
    \node [n,label=$\Lambda$] (zero){};
    \node [n] (zero_) [below=\edge of zero] {};
    \node [n,label={\texttt u}] (u) [right=\dist of zero] {};
    \node [n] (u_) [below=\edge of u] {};
    \node [n,label={\texttt v}] (v) [right=\dist of u] {};
    \node [n] (v_) [below=\edge of v] {};
    \node [n,label=\texttt{w}] (w) [right=\dist of v] {};
    \node [n] (w_) [below=\edge of w] {};
    \node [n] (zero__) [below=\edge of zero_]{};
    \node [n] (u__) [below=\edge of u_]{};
    \node [n] (v__) [below=\edge of v_]{};
    \node [n] (w__) [below=\edge of w_]{};
    \node [n] (zero___) [below=\edge of zero__]{};
    \node [n] (u___) [below=\edge of u__]{};
    \node [n] (v___) [below=\edge of v__)]{};
    \node [n] (w___) [below=\edge of w__]{};  
    \node [n] (zero____) [below=\edge of zero___]{};
    \node [n] (u____) [below=\edge of u___]{};
    \node [n] (v____) [below=\edge of v___)]{};
    \node [n] (w____) [below=\edge of w___]{};

@@

\subsubsection{Overview of the IDE Algorithm}\label{sec:ideoverview}
Just as any distributive function from $2^D$ to $2^D$ can be represented with a
representation relation, it is also possible to represent any distributive functions from
$\textsf{Env}(D,L)$
to
$\textsf{Env}(D,L)$
with a \textit{pointwise representation}. A pointwise representation is a bipartite graph
with the same nodes~\footnote{The IDE literature uses the symbol $\Lambda$ for the node that
    is denoted $\mathbf0$ in the IFDS literature.}
and edges as a representation relation, except that each edge is labelled
with a \textit{micro-function}, which is a function from $L$ to $L$. 
\commentout{
The pointwise representation of an environment transformer 
$t : \textsf{Env}(D,L) \to \textsf{Env}(D,L)$
is defined as
\newcommand{\microedge}[3]{#1\xrightarrow{#3}#2}
\begin{align*}
    R_t =& \{ \microedge{\Lambda}{\Lambda}{\lambda l.l} \} \cup
    \{\microedge{\Lambda}{d_j}{\lambda l.t(\Omega)(d_j)} \mid d_j \in D\}\\
    &\cup
    \{\microedge{d_i}{d_j}{\lambda l.t(\Omega[d_i\to l])(d_j)} \mid d_i, d_j \in D\}.
\end{align*}
}
Let $\Omega = \lambda d.\top$ be the environment that maps every element of $D$ to $\top$.
\ftodo{
   What is the relationship between $\Omega$ and $\Delta$?
}
\otodo{What do you mean by $\Delta$?}
Thanks to distributivity, every environment transformer 
$t : \textsf{Env}(D,L) \to \textsf{Env}(D,L)$
can be decomposed into its effect on $\Omega$ and on a set of environments $\Omega[d_i\to l]$
that map every element except one ($d_i$) to $\top$:
\[
    t(m)(d_j) = \lambda l. t(\Omega)(d_j) \sqcap \bigsqcap_{d_i\in D} \lambda l. t(\Omega[d_i\to l])(d_j).
\]
The functions $\lambda l. \cdots$ in this decomposition are the micro-functions that
appear on the edges of the pointwise representation edges from $\Lambda$ to each $d_j$ and from
each $d_i$ to each $d_j$.%
\footnote{The IDE paper defines a more complicated but equivalent set of micro-functions
that eliminate some duplication of computation.}
The absence of an edge in the pointwise representation from some $d_i$ to some $d_j$ is
equivalent to an edge with micro-function $\lambda l.\top$.

\otodo{Discuss the micro-functions in the example exploded supergraph in Figure 3.}

@@

Similar to the IFDS algorithm, a practical implementation of the IDE algorithm requires
the input dataflow functions to be provided in their pointwise representation
as exploded supergraph edges labelled with micro-functions.
\mtodo{Should we cite the ``Practical extensions'' paper here that talks about the on-demand IFDS algorithm?}
Specifically,
the input is generally provided as a function $f: N^* \times D \times N^* \to (D \to F)$,
where $F$ is the set of representations of micro-functions from $L$ to $L$.
Given a (non-exploded) supergraph edge $n \to n'$ and a dataflow fact $d$,
$f(n,d,n')$ returns a map that gives, for each fact $d'$, the micro-function $f$
that appears on the exploded supergraph edge $(n,d) \to (n',d')$.
Like in the IFDS algorithm, the function $f$ can be split up into separate functions that handle the cases when
the $n\to n'$ is an intraprocedural edge, a call-to-start edge, or an end-to-return edge.

@@

\mtodo{I think the rest of this section will not make sense to anyone who does not already understand it. Should I try to replace it with one paragraph that tries to give an intuitive understanding of what the IDE algorithm is doing?}
The overall idea behind computing the lattice elements $l_{n,\,d}$ is the following. For each inter-procedurally realizable path
\[
  p=\left[(\startmain,\,\Lambda),\,(n_1,\,d_1),\,\dots,\,(n_k,\,d_k)\right]
\]
 that starts with the entrypoint of the exploded supergraph, we compute the micro function $f_p$ that corresponds to $p$. The micro function consists of the composition of all individual micro functions with which the edges of $p$ are labeled:
\begin{align}
  f_p=\textsf{EdgeFn}((n_{k-1},\,d_{k-1}),\,(n_k,\,d_k))\,\circ\ldots\circ
      \textsf{EdgeFn}(\startmain,\,\Lambda),\,(n_1,\,d_1))\,.
\end{align}

@@

\ftodo{Would it make sense to discuss an example of an IDE problem here?  Perhaps we can do this
  without using much space by referring to an existing figure elsewhere in the paper?}
\otodo{I have the todo on the previous page to add text referring to the example in Figure 3.}

>>>>

\section{Background}\label{sec:bg}
%The purpose of the correlated-calls analysis is to solve IFDS problems more precisely than using the standard IFDS algorithm by ruling out some infeasible paths. The correlated-calls analysis works by transforming an IFDS problem to an IDE problem, solving the IDE problem, and transforming the IDE result to a solution to the original IFDS problem. 
This section defines basic terminology and presents the IFDS and IDE algorithms.
%\ftodo{
  %Shall we add a sentence saying that readers familiar with these algorithms may skip this section?
%}

\subsection{Terminology and Notation}
%We will start by introducing several concepts used by the IFDS and IDE analyses.
%\begin{mdelete}\mtodo{We already say (but less precisely) what a CFG is in the introduction.}
The \textit{control-flow graph} of a procedure is a directed graph whose nodes are instructions, and which contains an edge from $n_1$ to $n_2$ whenever
$n_2$ may execute immediately after $n_1$. A CFG has a distinguished \textit{start node} \textsf{start}$_p$ and \textit{end node} \textsf{end}$_p$.
Following the presentation of \cite{reps1995precise,sagiv1996precise}, we follow every
call instruction with a no-op instruction, so that every \textit{call node} is immediately
followed by a \textit{return node} in the CFG.
%\end{mdelete}
%and edges represent transfer of control between the instructions during an execution of the program. 
%A control-flow graph has a unique start node, $\startmain$, which is the node corresponding to the program entrypoint.
%An \textit{intra-procedural} path is a path in a control-flow graph whose nodes are in the same procedure. By contrast, an \textit{inter-procedural path} is one that contains nodes from different procedures. 
The \textit{control-flow supergraph} of a program contains the CFGs of all of the procedures as
subgraphs. In addition, for each call instruction $c$, the supergraph contains a \textit{call-to-start} edge to the start node of every procedure that
may be called from $c$, and an \textit{end-to-return} edge from the end node of the procedure back to the call instruction.
%\otodo{do we really need to extra "return nodes" that the IFDS/IDE papers add?}
%is a control-flow graph
%in which each procedure $p$ is augmented with an additional \textit{start node} \textsf{start}$_p$ and \textit{end node} \textsf{end}$_p$, and for each call $c_q$ to a procedure $q$, there is a \textit{call node} \textsf{call}$_{c_q}$ and subsequent \textit{return node} \textsf{return}$_{c_q}$.

@@

%\otodo{do we ever use $\src$ and $\target$?}
We denote the source and end nodes of a graph edge $e$ as $\src e$ and $\target e$.

@@

A path through the control-flow supergraph is \textit{valid} if it follows the usual stack-based calling 
discipline: every end-to-return edge on the path returns
to the site of the most recent call that has not yet been matched by a return. 
%\ftodo{Can we explain/define the notion of the ``most recent unmatched call'' more precisely?}
The set of all valid paths from the program entry point to
a node $n$ is denoted $\ivp(n)$.
%\otodo{Should we give a formal definition?}

@@

%\otodo{The definitions that Marianna had were for \emph{complete}
%lattices/semilattices. All of the lattices in the context of IFDS/IDE
%are/must be complete. I'll just say that here.}
%\ftodo{Would it make sense to first the define the notion of a lattice without referring to its completeness?
       %This could be followed by defining what it means for a (semi)lattice to be complete, and then we
       %could say that all lattices considered in this paper are complete, etc.}
%\ftodo{Can we define the symbols $\sqcup$ and $\sqcap$ for join and meet here?}
A \textit{lattice}%
\footnote{The definitions that we give here are of \textit{complete} lattices and semilattices.
Since all of the (semi)lattices discussed in this paper are required to be complete, we omit the
\textit{complete} qualifier.}
is a partially ordered set $(S,\sqsubseteq)$ in which every subset has a least upper bound, called \textit{join} or $\sqcup$, and a greatest lower bound, called \textit{meet} or $\sqcap$.
A \textit{meet semilattice} is a partially ordered set in which every subset need only have a greatest lower bound.
The symbols $\bot$ and $\top$ are used to denote the greatest lower bound of $S$ and of the empty set, respectively.

@@

%On the exploded graph, the composition of two functions is represented by the paths that are formed when the exploded-graph edges are combined.
%\otodo{The example used to say $R_f \circ R_g$, but I believe it showed $R_g \circ R_f$. I fixed it, but please check that this is correct.}

@@

In this way, the IFDS algorithm reduces the input data-flow problem to a graph-reachability problem.
\begin{example}
  In a taint analysis, $D$ is the set of variables in the program. If a fact $d\in D$ is reachable at a given node, then the variable is considered secret at that node. Otherwise, it is considered not secret. The question ``is $d$ secret at node $n$?'' becomes ``is there a realizable path from (\textsf{start}$_\texttt{main}$,\,\textbf{0}) to $(n,\,d)$?''.
\end{example}
\commentout{\begin{example} 
  In an available-expressions analysis, $D$ is the set of all expressions in the program. If an expression $d\in D$ is reachable at a certain node, it means that it does not need to be recomputed at that node. 
\end{example}}
}

\input{figures/fig-cc_edge_fn_example}
%\mtodo{In Figure~\ref{fig:cc_edgefn_example}, should we say that $\psi$ corresponds to the function's return value?}
\begin{example}
  The exploded supergraph for Listing~\ref{list:ccexample} is shown in Figure~\ref{fig:cc_edgefn_example}.
  The labels on the edges will be explained in Section~\ref{sec:bgide}
  We can see that there is a realizable path
  from the start node of the exploded graph to the variable \verb's' at~the~node~$\textsf{print(s)}$ in the \verb'B.bar' method. This means that at that node, \verb's' is considered secret.

@@

\begin{figure}
  \centering
    \tikzstyle{n}=[fill=black,circle,inner sep=1.5pt,sm]
    \tikzstyle{sm}=[font=\footnotesize]
\begin{tikzpicture}[>=stealth,on grid, auto]
    \node [n,label=$\mathbf0$] (zero){};
    \node [n] (zero_) [below=\edge of zero] {};
    \node [n,label={\texttt u}] (u) [right=\dist of zero] {};
    \node [n] (u_) [below=\edge of u] {};
    \node [n,label={\texttt v}] (v) [right=\dist of u] {};
    \node [n] (v_) [below=\edge of v] {};
    \node [n,label=\texttt{w}] (w) [right=\dist of v] {};
    \node [n] (w_) [below=\edge of w] {};
    \node [n] (zero__) [below=\edge of zero_]{};
    \node [n] (u__) [below=\edge of u_]{};
    \node [n] (v__) [below=\edge of v_]{};
    \node [n] (w__) [below=\edge of w_]{};
    \node [n] (zero___) [below=\edge of zero__]{};
    \node [n] (u___) [below=\edge of u__]{};
    \node [n] (v___) [below=\edge of v__)]{};
    \node [n] (w___) [below=\edge of w__]{};  
    \node [n] (zero____) [below=\edge of zero___]{};
    \node [n] (u____) [below=\edge of u___]{};
    \node [n] (v____) [below=\edge of v___)]{};
    \node [n] (w____) [below=\edge of w___]{};

@@

\subsubsection{Overview of the IDE Algorithm}\label{sec:ideoverview}
Just as any distributive function from $2^D$ to $2^D$ can be represented with a
representation relation, it is also possible to represent any distributive functions from
$\textsf{Env}(D,L)$
to
$\textsf{Env}(D,L)$
with a \textit{pointwise representation}. A pointwise representation is a bipartite graph
with the same nodes~\footnote{The IDE literature uses the symbol $\Lambda$ for the node that
    is denoted $\mathbf0$ in the IFDS literature. We use $\mathbf0$ throughout this paper for consistency.}
and edges as a representation relation, except that each edge is labelled
with a \textit{micro-function}, which is a function from $L$ to $L$. 
\commentout{
The pointwise representation of an environment transformer 
$t : \textsf{Env}(D,L) \to \textsf{Env}(D,L)$
is defined as
\newcommand{\microedge}[3]{#1\xrightarrow{#3}#2}
\begin{align*}
    R_t =& \{ \microedge{\mathbf0}{\mathbf0}{\lambda l.l} \} \cup
    \{\microedge{\mathbf0}{d_j}{\lambda l.t(\Omega)(d_j)} \mid d_j \in D\}\\
    &\cup
    \{\microedge{d_i}{d_j}{\lambda l.t(\Omega[d_i\to l])(d_j)} \mid d_i, d_j \in D\}.
\end{align*}
}
Let $\Omega = \lambda d.\top$ be the environment that maps every element of $D$ to $\top$.
%\ftodo{
   %What is the relationship between $\Omega$ and $\Delta$?
%}
%\otodo{What do you mean by $\Delta$?}
Thanks to distributivity, every environment transformer 
$t : \textsf{Env}(D,L) \to \textsf{Env}(D,L)$
can be decomposed into its effect on $\Omega$ and on a set of environments $\Omega[d_i\to l]$
that map every element except one ($d_i$) to $\top$:
\[
    t(m)(d_j) = \lambda l. t(\Omega)(d_j) \sqcap \bigsqcap_{d_i\in D} \lambda l. t(\Omega[d_i\to l])(d_j).
\]
The functions $\lambda l. \cdots$ in this decomposition are the micro-functions that
appear on the edges of the pointwise representation edges from $\mathbf0$ to each $d_j$ and from
each $d_i$ to each $d_j$.%
\footnote{The IDE paper defines a more complicated but equivalent set of micro-functions
that eliminate some duplication of computation.}
The absence of an edge in the pointwise representation from some $d_i$ to some $d_j$ is
equivalent to an edge with micro-function $\lambda l.\top$.

%\otodo{Discuss the micro-functions in the example exploded supergraph in Figure 3.}
\begin{example}
    In the exploded supergraph in Figure~\ref{fig:cc_edgefn_example},
    the micro-functions are shown as labels on the graph edges.
    Every edge without an explicit label has the identity as its
    micro-function. The micro-functions on the three edges from
    the node \verb+return secret()+ to the node $\texttt{end}_\texttt{A.foo}$
    together represent the environment transformer 
    $\lambda e.e[\psi \to \lambda m.\bot \sqcap \lambda m.m]$.

    To eliminate infeasible paths due to correlated calls, we encode the taint
    analysis using environments $\textsf{Env}(D,L)$, where $D$ is the set of
    variables and $L$ is a map from receiver variables to sets of possible
    types. The interpretation of such an environment $e$ is that a given variable
    $v \in D$ may contain a secret value in an exeuction in which the runtime
    types of the objects pointed to be the receiver variables are in the sets
    specified by $e(v)$.
\end{example}

@@

Similar to the IFDS algorithm, a practical implementation of the IDE algorithm requires
the input dataflow functions to be provided in their pointwise representation
as exploded supergraph edges labelled with micro-functions.
%\mtodo{Should we cite the ``Practical extensions'' paper here that talks about the on-demand IFDS algorithm?}
Specifically,
the input is generally provided as a function $f: N^* \times D \times N^* \to (D \to F)$,
where $F$ is the set of representations of micro-functions from $L$ to $L$.
Given a (non-exploded) supergraph edge $n \to n'$ and a dataflow fact $d$,
$f(n,d,n')$ returns a map that gives, for each fact $d'$, the micro-function $f$
that appears on the exploded supergraph edge $(n,d) \to (n',d')$.
Like in the IFDS algorithm, the function $f$ can be split up into separate functions that handle the cases when
the $n\to n'$ is an intraprocedural edge, a call-to-start edge, or an end-to-return edge.

@@

\mtodo{I think the rest of this section will not make sense to anyone who does not already understand it. Should I try to replace it with one paragraph that tries to give an intuitive understanding of what the IDE algorithm is doing?}
The overall idea behind computing the lattice elements $l_{n,\,d}$ is the following. For each inter-procedurally realizable path
\[
  p=\left[(\startmain,\,\mathbf0),\,(n_1,\,d_1),\,\dots,\,(n_k,\,d_k)\right]
\]
 that starts with the entrypoint of the exploded supergraph, we compute the micro function $f_p$ that corresponds to $p$. The micro function consists of the composition of all individual micro functions with which the edges of $p$ are labeled:
\begin{align}
  f_p=\textsf{EdgeFn}((n_{k-1},\,d_{k-1}),\,(n_k,\,d_k))\,\circ\ldots\circ
      \textsf{EdgeFn}(\startmain,\,\mathbf0),\,(n_1,\,d_1))\,.
\end{align}

@@

\ftodo{Would it make sense to discuss an example of an IDE problem here?  Perhaps we can do this
  without using much space by referring to an existing figure elsewhere in the paper?}
  \otodo{See Example 4 on the previous page.}

### 2014-12-15 content/datastr.tex
one more delete
pass through section 3

We can now show how the correlated-calls definitions of the meet and composition operations on micro functions allow us to detect infeasible paths in a program.
\begin{example}\label{ex:cc}
  The edges of the exploded supergraph in Figure~\ref{fig:cc_edgefn_example} correspond to the edges of an IFDS taint analysis. We can see that there is a path from the node $(\highlight{\startmain}{greyblue},\,\Lambda)$ to $(\highlight{\texttt{print(s)}}{lightsalmonpink},\,\texttt s)$. This means that the IFDS taint analysis considers \texttt s to be a secret value that is leaked at the print statement.

@@

\paragraph{Final Remarks}

@@

Second, a composition $f$ of two functions $f_1$ and $f_2$ would have to store both $f_1$ and $f_2$. For instance, if $f_1=\lambda x\,.\,x+1$ and $f_2=\lambda x\,.\,x+2$, then $f=f_2\circ f_1$ would be represented as 
\[
  f=\lambda x\,.\,(\lambda y\,.\,y+2)((\lambda z\,.\,z+1)\,x)
\]
instead of
\[
  f=\lambda x\,.\,x+3.
\]
Having a compact representation for function composition is especially important for the first phase of the IDE algorithm, in the computation of jump functions~\cite{sagiv1996precise}. The same argument applies to computing function meets.

>>>>

We can now show how the correlated-calls definitions of the meet and composition operations on micro functions allow us to detect infeasible paths in a program.
\begin{example}\label{ex:cc}
  The edges of the exploded supergraph in Figure~\ref{fig:cc_edgefn_example} correspond to the edges of an IFDS taint analysis. We can see that there is a path from the node $(\highlight{\startmain}{greyblue},\,\mathbf0)$ to $(\highlight{\texttt{print(s)}}{lightsalmonpink},\,\texttt s)$. This means that the IFDS taint analysis considers \texttt s to be a secret value that is leaked at the print statement.

@@

\begin{mdelete}
\paragraph{Final Remarks}

@@

Second, a composition $f$ of two functions $f_1$ and $f_2$ would have to store both $f_1$ and $f_2$. For instance, if $f_1=\lambda x\,.\,x+1$ and $f_2=\lambda x\,.\,x+2$, then $f=f_2\circ f_1$ would be represented as 
\[
  f=\lambda x\,.\,(\lambda y\,.\,y+2)((\lambda z\,.\,z+1)\,x)
\]
instead of
\[
  f=\lambda x\,.\,x+3.
\]
Having a compact representation for function composition is especially important for the first phase of the IDE algorithm, in the computation of jump functions~\cite{sagiv1996precise}. The same argument applies to computing function meets.
\end{mdelete}

### 2014-12-15 content/impl.tex
removing crossreferences, adding comment
pass through section 3

\input{figures/fig-cc_edge_fn_example}

\otodo{we agreed to move this figure to the initial example section}

@@

%\paragraph{Converting IFDS problems to IDE problems}
%Since IDE is a generalization of IFDS, any IFDS problem can be converted into an equivalent IDE problem~\cite{sagiv1996precise}.
The lattice
for the equivalence transformation $\transEq$ 
is the two-point lattice
    $L^\equiv=\{\bot,\ \top\}$,
where $\bot$ means ``reachable'', and $\top$ means ``not reachable''. 
The edge functions $\edgefn^\equiv$ are defined as
\begin{equation}
    \edgefn^\equiv=
    \begin{cases}
      \lambda e\,.\,\lambda m\,.\,\bot&\text{if $d_1(e)=\Lambda$ and $d_2(e)\ne\Lambda$;}\\
      \lambda e\,.\,\id&\text{otherwise,}
    \end{cases}
\end{equation}
where $d_1(e)$ is the source fact of an edge $e$ and $d_2(e)$ is its target fact. 
At a~``diagonal'' edge from a $\Lambda$-fact to a non-$\Lambda$-fact
$d$, the micro function returns $\bot$
to make
the fact $d$ reachable. All other micro-functions are the identity\mtodo{``the identity function'' or is it okay ot just say ``the identity''?}.
The equivalence transformation is thus defined as:
  $\transEq((G^\#))=(G^\#,\,L^\equiv,\,\mathsf{EdgeFn}^\equiv)$.

@@

In the correlated-calls transformation lattice $\lcc$, a map that maps any receiver
to the empty set of possible types means that the corresponding data flow path is
infeasible. Therefore, a result $\rho=\resultIDE(\transCC _S(P))$ of the correlated-calls IDE analysis is
converted to an IFDS result as follows:
\begin{equation}\label{eq:transCcDef}
  \backCC(\rho) = \lambda n.\{d\mid\forall r\in S\,.\,\rho(n)(d)\neq\top_T\}.
\end{equation}

>>>>

@@

%\paragraph{Converting IFDS problems to IDE problems}
%Since IDE is a generalization of IFDS, any IFDS problem can be converted into an equivalent IDE problem~\cite{sagiv1996precise}.
The lattice
for the equivalence transformation $\transEq$ 
is the two-point lattice
    $L^\equiv=\{\bot,\ \top\}$,
where $\bot$ means ``reachable'', and $\top$ means ``not reachable''. 
The edge functions $\edgefn^\equiv$ are defined as
\begin{equation}
    \edgefn^\equiv=
    \begin{cases}
      \lambda e\,.\,\lambda m\,.\,\bot&\text{if $d_1(e)=\Lambda$ and $d_2(e)\ne\Lambda$;}\\
      \lambda e\,.\,\id&\text{otherwise,}
    \end{cases}
\end{equation}
where $d_1(e)$ is the source fact of an edge $e$ and $d_2(e)$ is its target fact. 
At a~``diagonal'' edge from a $\Lambda$-fact to a non-$\Lambda$-fact
$d$, the micro function returns $\bot$
to make
the fact $d$ reachable. All other micro-functions are the identity function.
%\mtodo{``the identity function'' or is it okay ot just say ``the identity''?}.
The equivalence transformation is thus defined as:
  $\transEq((G^\#))=(G^\#,\,L^\equiv,\,\mathsf{EdgeFn}^\equiv)$.

@@

In the correlated-calls transformation lattice $\lcc$, a map that maps any receiver
to the empty set of possible types means that the corresponding data flow path is
infeasible. Therefore, a result $\rho=\resultIDE(\transCC S(P))$ of the correlated-calls IDE analysis is
converted to an IFDS result as follows:
\begin{equation}\label{eq:transCcDef}
  \backCC(\rho) = \lambda n.\{d\mid\forall r\in S\,.\,\rho(n)(d)\neq\top_T\}.
\end{equation}

### 2014-12-15 content/related.tex
eliminate TODOs in introduction; improve formatting of title
pass through section 3

\section{Related Work}
\otodo{Should we remove first initials in this section?}
The IFDS algorithm is an instance of the functional approach to data-flow analysis developed by Sharir and Pnueli~\cite{pnueli1981two}.
\commentout{
Their algorithm is based on computing \textit{summary functions} that return the data-flow value at the end of a procedure, given the data-flow value at the start of the procedure. IFDS problems form a more restricted set of data-flow problems: unlike in the functional approach, IFDS flow functions have to be distributive, and the set of data-flow facts $D$ has to be finite. However, the IFDS algorithm is more general than Sharir's and Pnueli's algorithm in that it can handle programs containing local variables and parameters in recursive methods.
}
IFDS has been used to encode a variety of data-flow problems such as typestate analysis%
\commentout{(determining which operations can be performed on an object at a given program point)}~\cite{naeem2008typestate,DBLP:conf/pldi/ZhangMGNY14} and shape analysis%
\commentout{(detecting errors and validating properties of programs at compile time)}%
~\cite{DBLP:conf/birthday/KreikerRRSWY13}. IFDS has been broadly used~\cite{DBLP:conf/pldi/ArztRFBBKTOM14,tripp2009taj} and extended~\cite{DBLP:conf/sigsoft/LerchHBM14} to solve taint-analysis problems.

>>>>

\section{Related Work}
  \label{sec:Related}
%\otodo{Should we remove first initials in this section?}
The IFDS algorithm is an instance of the functional approach to data-flow analysis developed by Sharir and Pnueli~\cite{pnueli1981two}.
\commentout{
Their algorithm is based on computing \textit{summary functions} that return the data-flow value at the end of a procedure, given the data-flow value at the start of the procedure. IFDS problems form a more restricted set of data-flow problems: unlike in the functional approach, IFDS flow functions have to be distributive, and the set of data-flow facts $D$ has to be finite. However, the IFDS algorithm is more general than Sharir's and Pnueli's algorithm in that it can handle programs containing local variables and parameters in recursive methods.
}
IFDS has been used to encode a variety of data-flow problems such as typestate analysis%
\commentout{(determining which operations can be performed on an object at a given program point)}~\cite{naeem2008typestate,DBLP:conf/pldi/ZhangMGNY14} and shape analysis%
\commentout{(detecting errors and validating properties of programs at compile time)}%
~\cite{DBLP:conf/birthday/KreikerRRSWY13}. IFDS has been broadly used~\cite{DBLP:conf/pldi/ArztRFBBKTOM14,tripp2009taj} and extended~\cite{DBLP:conf/sigsoft/LerchHBM14} to solve taint-analysis problems.
